---
title: "**BIOL365** — Marine and Terrestrial Ecology"
author: Dr James B Dorey, University of Wollongong
output: github_document
urlcolor: blue

editor_options: 
  markdown: 
    wrap: 80
---

<!-- badges: start -->

[![License](https://img.shields.io/badge/license-GPL%20(%3E=%203)-lightgrey.svg?style=flat)](http://www.gnu.org/licenses/gpl-3.0.html)

<!-- badges: end -->

```{r websiteSetUp, eval = FALSE, include=FALSE}
setwd("/Users/jamesdorey/Desktop/Uni/Teaching/EvolutionPracs")

  # Setup github pages 
  # See https://happygitwithr.com/common-remote-setups.html 
  # AND see https://pkgdown.r-lib.org/index.html
# Do this only once
# usethis::use_git("jbdorey/EvolutionPracs")
  
# Run once to configure your package to use and deploy pkgdown
# usethis::use_pkgdown_github_pages()

# Preview your site locally before publishing EACH TIME... check description for dependencies and check Actions on Github
pkgdown::build_site(pkg = "/Users/jamesdorey/Desktop/Uni/Teaching/EvolutionPracs",
                    devel = FALSE)
usethis::use_github_action("pkgdown")
usethis::use_git_remote("origin", url = NULL, overwrite = TRUE)
usethis::use_github(private = FALSE)
# Run a check 
devtools::check()
```

```{r setup, include=FALSE}
library(readr)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


### University of Wollongong

#### **Overview**
This is a simple GitHub page to host some activities for the BIOL365 cohort. It includes the Weeks one through five practicals and some associated files.

## Directory
* [Evolution Prac 1 — Getting ready!](https://jbdorey.github.io/EvolutionPracs/articles/PhyloPrac1.html)
* [Evolution Prac 2 — Access genetic data from GenBank](https://jbdorey.github.io/EvolutionPracs/articles/PhyloPrac2.html)
* [Evolution Prac 3 — Aligning genetic data and building phylogenies in R](https://jbdorey.github.io/EvolutionPracs/articles/PhyloPrac3.html)
* [Evolution prac 4 — Macroevolutionary questions!](https://jbdorey.github.io/EvolutionPracs/articles/PhyloPrac4.html)
* [Evolution prac 5 — Tips and pitfalls](https://jbdorey.github.io/EvolutionPracs/articles/PhyloPrac5.html)


## Authors

Contributors names and contact info

Dr [James Dorey](https://scholars.uow.edu.au/james-dorey), jdorey@uow.edu.au, 
[@jamesbeedorey.bsky.social]([https://twitter.com/dompizzie](https://bsky.app/profile/jamesbeedorey.bsky.social))

## Version History

* 1.0
    * Initial Release and fixes